---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ScatterLinePlot

<!-- badges: start -->
<!-- badges: end -->

The goal of ScatterLinePlot is to create scatterplots with lines, grouped by a variable. It is a convenient function that creates a scatterplot with each point connected by a line and is grouped based on a specified variable and also filters out any NA values in the y-variable. The following package uses 'dplyr' and 'ggplot2' in order to create the plot. You provide the dataset, group variable, x variable, and y variable then it graphs it for you.

## Installation

You can install the development version of ScatterLinePlot from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/ScatterLinePlot")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r}
# Load required packages (if not already loaded)
library(ScatterLinePlot)
library(ggplot2)
library(dplyr)

# Create a sample data frame
df <- data.frame(
  Group_var = rep(letters[1:3], each = 4),
  X_var = rep(1:4, times = 3),
  Y_var = c(3, 5, 2, 6, 4, 7, NA, 8, 1, 3, 9, 4)
)

# Create a scatterplot with lines connecting points
ScatterLinePlot(df, Group_var, X_var, Y_var)
```

